---
title: "DV_RProject2: Visualizations From Narcisstic Personality Inventory (NPI) Test"
author: "Syairah Ridzuan, Madeline Packard, Arthur DeVitalis"
date: "February 15, 2015"
output: html_document
---

The Narcisstic Personality Inventory (NPI) is created by Raskin and Hall (1979) and is designed to evaluate the narcisstic expressions that are frequently conveyed in normal circumstances. Thus, those who obtain high scores in this test are not necessarily diagnosed with Narcisstic Personality Disorder (NPD).


**Pulling the Data Set from Oracle Database**

The data set pulled from the Oracle database includes the participant's answers to all forty questions, along with all participant's age, gender, time elapsed, and score on the test.

```{r, include=FALSE, results = "hide"}
source("../01 Data/packages.R", echo = FALSE)
```
```{r}
source("../01 Data/full_df.R", echo = TRUE)
```

```{r, include=FALSE, results = "hide"}
source("../01 Data/column_rename.R", echo = FALSE)
```

The data set is too large to display all 44 columns in this HTML document, thus the following shows a subset of the dataframe that are just loaded into R.

```{r}
source("../01 Data/display_subset.R", echo = TRUE)
```

### Visualizations

Once we have the data loaded from oracle, we can begin visualizing different data subsets. One interesting observation would be to see the distribution of scores across the number of participants.

```{r}
source("../02 Visualizations/score_dist.R", echo = TRUE)
```

This visualization shows that the majority participants scored between 7 and 18. A median number around 600 participants answered around 10 narcissistic tendency questions on average. **Participants had an overall average score of**. 

```{r}
source("../02 Visualizations/tendency_by_age_gender.R", echo = TRUE)
```



In this graph, gender is identified as: 0 = Not Identified, 1 = Male, 2 = Female, 3 = Other.

The plot shows that overall narcissim decreases slightly with age, regardless of gender. The negative correlation shows narcissistic expressions appears to be more frequent with the younger generation.

The boxplot below shows a clearer relationship between gender and score.

```{r}
source("../02 Visualizations/boxplot_score_gender.R", echo = TRUE)
```

Women have a higher median NPI score compared to men. The median score range of men is lower but has more outliars. Though it is a wider distritubution of scores for women compared to other genders. 

```{r}
source("../01 Data/modified_df.R", echo = TRUE)
```

These are the responses for all the questions. **Numbers of parcipants versus gender versus question responses.**  

```{r}
source("../02 Visualizations/participants_response_allQs.R", echo = TRUE)
```

We're interested to see what questions received non-responses, so we took a subset of the modified dataframe to help visualize the results. 

```{r}
source("../01 Data/subsetof_modified_df.R", echo = TRUE)
```
We did a preliminary observation of all the non-response questions. 

```{r}
source("../02 Visualizations/allquestions_nonresponse.R", echo = TRUE)
```
Questions 35, 30, and 12 had the highest to lowest rate of not being answered. Ambiguity on taking orders and giving them is interesting on question 12. 

```{r}
source("../02 Visualizations/nonresponse_bygender.R", echo = TRUE)
```
We were curious about non-responses by gender so we plotted this. It is important to note that there is not a 0 row because participants who did not identify their gender answered all questions in this case. 

Both males and females had a high rate of non-response on question 35, but almost 40 women skipped compared to 26 men:
 Q35: 1=People sometimes believe what I tell them. 2=I can make anybody believe anything I want them to.
Similarly, more women left these questions unanswered than men: 
Q17. 1=If I feel competent I am willing to take responsibility for making decisions. 2=I like to take responsibility for making decisions.

Men were less significantly responsive compared to women on these questions:
 Q11. 1=I am assertive. 2=I wish I were more assertive.
 Q17. 1=If I feel competent I am willing to take responsibility for making decisions. 2=I like to take responsibility for making decisions.
 Q24. 1=I expect a great deal from other people. 2=I like to do things for other people.





