---
title: "DV_RProject2: Visualizations From Narcisstic Personality Inventory (NPI) Test"
author: "Syairah Ridzuan, Madeline Packard, Arthur DeVitalis"
date: "February 15, 2015"
output: html_document
---

The Narcisstic Personality Inventory (NPI) is created by Raskin and Hall (1979) and is designed to evaluate the narcisstic expressions that are frequently conveyed in normal circumstances. Thus, those who obtain high scores in this test are not necessarily diagnosed with Narcisstic Personality Disorder (NPD).


**Pulling the Data Set from Oracle Database**

The data set pulled from the Oracle database includes the participant's answers to all forty questions, along with all participant's age, gender, time elapsed, and score on the test.

```{r, include=FALSE, results = "hide"}
source("../01 Data/packages.R", echo = FALSE)
```
```{r}
source("../01 Data/full_df.R", echo = TRUE)
```

```{r, include=FALSE, results = "hide"}
source("../01 Data/column_rename.R", echo = FALSE)
```

The data set is too large to display all 44 columns in this HTML document, thus the following shows a subset of the dataframe that are just loaded into R.

```{r}
source("../01 Data/display_subset.R", echo = TRUE)
```

### Visualizations

Once we have the data loaded from oracle, we can begin visualizing different data subsets. One interesting observation would be to see the distribution of scores across the number of participants.

```{r}
source("../02 Visualizations/score_dist.R", echo = TRUE)
```

This visualization shows that the majority participants scored between 7 and 18.
